Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging

### 2022-12-22 script/manuscript_MEE.Rmd
some discussion flex

**overall stuff and things**
We have demonstrated how a533 data may be used for plant barcoding in a metagenomic context. This was exemplified in an ecologically realistic situation, centered both in a context which serves as an immediate framework for land management studies,  and which produced fundamental natural history information. These datasets included taxonomically difficult clades (e.g. Mertensia, Lupinus) .

These results show that the overall results between **Bumble Bee ecology  ** observational and barcoding are largely congruent. But that ...

**Spatial ... & Timing ** (filters!)
- Fewer modelling runs for SDM's likely to be effective for determining inclusion, elastic inclusion criteria.
- The actual dataset which was used for training and testing all of the models incorporated into SDM's represented only roughly one quarter of the records available for such purposes. We consciously chose to do this in order to showcase the possibility of this approach working in less data rich areas. 
- Used fine scale flora to evaluate results of modelling, similar approaches based on quick field surveys which do not require comprehensive floristic endeavors.
- Timing in other areas may suffer complications due to lacking as strong a signal as that induced by snowmelt, but longer durations of flowering likely to help. 
- Sample size in phenology estimates had an effect which is likely to be maintained across all results.
- Regardless both show good agreement on flower onset, peak flowering, and moderate agreement with flowering cessation. The disagreement in flowering cessation is perhaps due to more microclimates which retain water, rather than microclimates which allow the early accumulation of heat. 
- Number of botanists rapidly decreasing no hope for much more field based information or funding.

@@

**CONCLUSIONS **

>>>>

**overall stuff and things**
We have demonstrated how Angiosperms533 data may be used for plant barcoding in a metagenomic context. This was exemplified in an ecologically realistic situation, centered both in a context which serves as an immediate framework for land management studies, and which produced fundamental natural history information. These datasets included closely related taxa in notoriously taxonomically difficult clades (e.g. *Mertensia*, *Lupinus*). We utilized spatial and temporal approaches for creating custom sequence databases which are readily applicable to any lab group with the capacity to perform next-generation sequencing across the entirety of multiple continents. In conjunction with well designed and implemented field based data collection we show how these methods may be widely used to test a variety of hypotheses related to ecological interactions.

These results show that the overall results between **Bumble Bee ecology** observational and barcoding are largely congruent. But that ...
Future analyses of the long term dataset... Global studies should aim to corroborate ...

**Spatial ... & Timing ** (filters!)
- Fewer modelling runs for SDM's likely to be effective for determining inclusion, elastic inclusion criteria per application.
- The actual dataset which was used for training and testing all of the models incorporated into SDM's represented only roughly one quarter of the records available for such purposes. We consciously chose to do this in order to showcase the possibility of this approach working in less data rich areas. 
- Used fine scale flora to evaluate results of modelling, similar approaches based on quick field surveys which do not require comprehensive floristic endeavors.
- Timing in other areas may suffer complications due to lacking as strong a signal as that induced by snowmelt, but longer durations of flowering likely to help. 
- Sample size in phenology estimates had an effect which is likely to be maintained across all results.
- Regardless both show good agreement on flower onset, peak flowering, and moderate agreement with flowering cessation. The disagreement in flowering cessation is perhaps due to more microclimates which retain water, rather than microclimates which allow the early accumulation of heat. 
- Number of botanists rapidly decreasing no hope for much more field based information or funding.

@@
